Put Title here

### 2018-11-21 General WLD combinatorics.tex
copied in the recursive cyclic intervals, but haven't edited it yet

\begin{rmk}
In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.  By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.  Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.  So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$ and no other propagator ends on the edge $(i+2, i+3)$.
\end{rmk}

@@

Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas

\begin{dfn}\label{protect dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$. In this case, $P_w(p) = \emptyset$. When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}. \eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
\end{enumerate}
\end{dfn}

The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$. Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$. We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$. \end{enumerate}

\begin{eg} \label{eg: protective sets}
Consider the admissible Wilson loop diagram
\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{17}{3}
	\drawnumbers
	\drawprop{1}{0}{16}{0}
	\drawlabeledprop{2}{0}{15}{1}{p}
    \drawprop{6}{2}{15}{0}
    \drawprop{3}{0}{6}{1}
    \drawprop{4}{0}{6}{0}
    \drawprop{7}{0}{11}{0}
    \drawprop{8}{0}{10}{0}
    \drawprop{11}{1}{14}{1}
    \drawprop{12}{0}{14}{0}
		\end{scope}
	\end{tikzpicture}
\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$. The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$. There is no set preventing $p$ from contributing $16$ to $I_{15}$. At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$. At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.

Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
\end{eg}

\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above. Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $. If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
\end{lem}

\begin{proof}
Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$. Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.

Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}. Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$. Then $s_x$ cannot contribute to $I_a$ before vertex $v$. By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$. Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$. Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$. In other words, $s_1$ has not been removed from the diagram at vertex $v$.

Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.

\begin{cor} \label{protecting cor}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
\end{cor}

\begin{proof}
Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
\end{proof}

The converse, however requires an extra condition.

\begin{lem} \label{protect conv lem}
For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp. $v+1$) to $I_a$.
\end{lem}

\begin{proof}
Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.

If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)

If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp. $i_{t_1}$ or $i_{t_1}+1$) to $I_a$. Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$. \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$. \item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}

However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$. One does this by a similar construction to above. In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.  By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.

We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction. For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction. That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$. Futher define $p_0 = p$.

%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}

If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.

If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
 \begin{description}

\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$. By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$. Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$. This leads to a contradiction.
\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
 \end{description} \note{correct but clear as mud? Help?}
\end{proof}

We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
\begin{prop}\label{res:alg k labels}
If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop}
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$. In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$. Suppose this doesn't happen, i.e. there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$. Without loss of generality, assume $a \leq_a i <_a j$. Otherwise, change the roles of $i$ and $j$.

Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.

However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
\end{proof}
\begin{comment}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

\end{proof}
\end{comment}

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.
\end{lem}

\begin{proof}
Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.

Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$. Write $k_{r+1}$ to be the counterclockwise most propagator with an end on the edge $j-1$, if it exists. If $r \geq 2$ or $r+1 = 2$, then both $P_j(p)$ and $P_{j+1}(p)$ exists for some subset of $a \in [n]$. If $r=1$ or $r+1= 2$ then only $P_j(p)$ exists. Otherwise, $P_j(p) = \emptyset$.

>>>>

\begin{rmk}
In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.  By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.  Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.  So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
\end{rmk}

@@

%Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
%\begin{dfn}\label{protect dfn}
%Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
%\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
%\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
%\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$. In this case, $P_w(p) = \emptyset$. When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
%\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}. \eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
%\end{enumerate}
%\end{dfn}
%The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$. Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$. We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$. \end{enumerate}
%\begin{eg} \label{eg: protective sets}
%Consider the admissible Wilson loop diagram
%\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
%	\begin{scope}
%	\drawWLD{17}{3}
%	\drawnumbers
%	\drawprop{1}{0}{16}{0}
%	\drawlabeledprop{2}{0}{15}{1}{p}
%    \drawprop{6}{2}{15}{0}
%    \drawprop{3}{0}{6}{1}
%    \drawprop{4}{0}{6}{0}
%    \drawprop{7}{0}{11}{0}
%    \drawprop{8}{0}{10}{0}
%    \drawprop{11}{1}{14}{1}
%    \drawprop{12}{0}{14}{0}
%		\end{scope}
%	\end{tikzpicture}
%\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$. The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$. There is no set preventing $p$ from contributing $16$ to $I_{15}$. At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$. At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
%Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
%\end{eg}
%\begin{lem}\label{protecting lem}
%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above. Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $. If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
%\end{lem}
%\begin{proof}
%Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$. Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
%Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}. Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$. Then $s_x$ cannot contribute to $I_a$ before vertex $v$. By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$. Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$. Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$. In other words, $s_1$ has not been removed from the diagram at vertex $v$.
%\end{proof}
%Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
%\begin{cor} \label{protecting cor}
%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
%\end{cor}
%\begin{proof}
%Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
%\end{proof}
%The converse, however requires an extra condition.
%\begin{lem} \label{protect conv lem}
%For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp. $v+1$) to $I_a$.
%\end{lem}
%\begin{proof}
%Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
%If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
%If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp. $i_{t_1}$ or $i_{t_1}+1$) to $I_a$. Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$. \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$. \item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
%However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$. One does this by a similar construction to above. In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.  By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
%We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction. For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction. That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$. Futher define $p_0 = p$.
%%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
%If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
%If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
% \begin{description}
%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$. By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$. Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$. This leads to a contradiction.
%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
% \end{description} \note{correct but clear as mud? Help?}
%\end{proof}
%We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
%\begin{prop}\label{res:alg k labels}
%If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
%\end{prop}
%\begin{proof}
%It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$. In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$. Suppose this doesn't happen, i.e. there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$. Without loss of generality, assume $a \leq_a i <_a j$. Otherwise, change the roles of $i$ and $j$.
%Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.

%However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
%\end{proof}

\note{This is a mess for now; protecting sets commented out, and 1.5 versions of the induction copied in by not yet edited}

This is the lemma from the email with the proof copied from the email.
\begin{lem}\label{lem last vert}
  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.  Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
\end{lem}

\begin{proof}
Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.  (This suffices because if $C(W)$ with the $n$th column removed had full rank but the lexicographically minimal basis of $C(W)$ included the $n$th column, then we'd obtain a contradiction by taking this minimal basis with the $n$th column removed and extending it to a basis using a column from the first $n-1$ columns of $C(W)$ which is possible by the full rank assumption.)

Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.  This is equivalent to an assignment of all propagators to supporting vertices so that no two are assigned to the same vertex and none are assigned to vertex $n$.  The lemma is proved if we show such an assignment exists.

Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.  If $f$ assigns $n$ propagators then we are done.  Otherwise there is a propagator $p$ which is not assigned but, by maximality, all of $p$s supporting vertices (other than possibly $n$) are assigned.  Build a sequence of sets $S_i$ of propagators and $T_i$ of vertices as follows.

\begin{enumerate}
  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \sup (\text{supp}(R) - \{n\})$.\label{item loop step}
  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not yet been assigned then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.  Do so, removing $q_{i+1}$'s old assignment.  This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.  This new assignment contradicts the maximality of $f$.
  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.  Thus $|S_{i+1}| = |T_{i+1}|+1$.  Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.  Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
  \item Increment $i$ and go to \label{itemp loop step}
\end{enumerate}

This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.  However, the only way for the process to end is by reaching a contradiction.  Therefore any maximal assignment is a basis not including column $n$ which proves the lemma.
\end{proof}

\note{This was commented out in the file: some (old?) version of the inductive argument?}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

\note{end of the piece that was commented out in the file}

\begin{lem} \label{vertex cyclic int lem}
  For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.

  \note{the above is the statement that was in this file, the below is the version of the statement from last july}

Let $p$ be a propagator of an admissible WLD $W$ on $n$ vertices.  Let $p = (i,j,k,l)$.  Let $J_p^{(W)}(i)$ be the indices $m$ where $I_m(p)=i$ and likewise for $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$.  Then $J_p^{(W)}(i)$, $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
\end{lem}

\begin{proof}
    We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.  Then by Lemma~\ref{lem sian} $W$ has at least one of the three situations illustrated in figure~\ref{fig 3 cases}

  \begin{figure}
    \includegraphics[scale=0.8]{3cases}
    \caption{Three cases for admissible WLDs with no unsupported vertices.  The blue highlighted region cannot support other propagators.  The green half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
  \end{figure}

In each of the three cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q$ with no other propagators inside it (although this region may or may not contain an unsupported vertex $b$). Call this diagram $V$ (figure \ref{fig V diagram}).

\begin{figure}
\includegraphics[scale=0.8]{Vdiagram}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q$. Vertex $b$ is omitted if we are considering the right hand case.}
\label{fig V diagram}
\end{figure}
